### 2017-03-29 Writing/device.tex
Update

Hardware informations are generally not considered interested in Internet traffic analysis attacks. In case of sensor network, such 
information might become be valuable. For example, hardware information might be exploited to identify devices with specific vulnerabilities, or can be used as a hint of what the target does and hence breaches the communication.

>>>>

The nature of sensor networks suggests that hardware information might became valuable in terms of security. For example, leakage of hardware information could help the adversary to identify devices with specific vulnerabilities, or provides hints of target's functionality which relates to the encrypted communication.
